Progress with the NOSAMS

### 2021-05-02 doc/SNEAP2021/SNEAP2021_HGIS_presentation/SNEAP2021_HGIS_presentation.Rmd
Update plot colors

dbds %>% 
  filter(Cur < 10) %>% 
  ggplot(aes(fm_consensus, fm_diff)) +
  geom_hline(yintercept = 0) +
  geom_pointrange(aes(ymin = fm_diff - merr, ymax = fm_diff + merr),
                 position = position_dodge2(width = .1),
                 size = .5) +
  labs(title = "Closed inlet",
       x = "Expected Fm",
       y = "Fm difference") +
  theme_classic() +
  theme_xaringan(title_font_size = 20,
                 text_font_size = 16,
                 background_color = "#ffffff")
```
]

@@

# flow vs time subplot
flow_time <- data.frame(x = 0:125) %>% 
  ggplot(aes(x)) +
  stat_function(fun=function(x) concCO2(x, r = 244) * 30, aes(color = "CO2")) +
  stat_function(fun=function(x) 30 - (concCO2(x, r = 244) * 30), aes(color = "Helium")) +
  scale_color_manual("Gas", values = c("green", "blue")) +
  labs(title = "Gas flows to source",
       subtitle = "7mL vial, 244μL/min helium, 30μL/min to source",
       y = "Gas flow (μL/min)") +
  theme_classic() +
  theme_xaringan(title_font_size = 20,
                 text_font_size = 18,
                 background_color = "#ffffff") +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        legend.position = c(0.87, 0.65),
        legend.background = element_rect(fill = "white", color = "black"))

# current vs time subplot
cur_time <- ggplot(data, aes(time, he12C)) +
  geom_smooth(span = .4, se=FALSE, color = "green") +
  geom_point() +
  xlim(0, 125) +
  labs(title = "Ion current",
       x = "Time (min)",
       y = "12C current (μA)") +
  theme_classic() +
  theme_xaringan(title_font_size = 20,
                 text_font_size = 18,
                 background_color = "#ffffff")

@@

.pull-right[
<br>
<br>
<br>
```{r cur-flow-os, fig.height=6, dev='svg'}
ggplot(data, aes(co2flow, he12C)) +
  geom_smooth(span = .3, se=FALSE, color = medium_blue) +
  geom_point() +
  labs(title = "Vial dillution current",
       subtitle = "250μL/min displacement, 30μl/min delivery",
       x = bquote('CO'[2]~'Flow (μl/min)'), 
       y = "12C current (μA)") +
  theme_classic() +
  theme_xaringan(title_font_size = 20,
                 text_font_size = 16,
                 background_color = "#ffffff")
```
]

@@

livefm_cur <- data %>% 
  filter(!(he12C < 2.5 & normFm > 1.05) & fm_consensus > 0.9) %>% 
  ggplot(aes(he12C, normFm)) + 
  geom_point() +
  xlim(0, xl) +
  ylim(.8, 1.2) +
  ggtitle("Ratio vs current") +
  theme_classic() +
  theme_xaringan(title_font_size = 20,
                 text_font_size = 18,
                 background_color = "#ffffff") +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        axis.text.x = element_blank())

deadfm_cur <- data %>% 
  filter(fm_consensus < 0.1 & normFm < 0.3 & Sample.Name != "DilDeadGas6") %>% 
  ggplot(aes(he12C, normFm)) + 
  geom_point() +
  xlim(0, xl) +
  ylim(0, .4) +
  xlab("12C Current (μA)") +
  theme_classic() +
  theme_xaringan(title_font_size = 20,
                 text_font_size = 18,
                 background_color = "#ffffff")

@@

```{r blank-model, fig.height = 4, dev='svg'}
# Plot of data and model with measured blanks
ggplot(ds, aes(Cur_inv, mean, color = Gas)) +
  geom_abline(slope = blankfit$LiveGas_Cur_inv, 
              intercept = blankfit$`LiveGas_(Intercept)`) +
  geom_abline(slope = blankfit$DeadGas_Cur_inv, 
              intercept = blankfit$`DeadGas_(Intercept)`) +
  geom_pointrange(aes(ymin = mean - merr, ymax = mean + merr), size = .3) + 
  xlim(0, 10) +
  labs(title = "Modelled blank",
       subtitle = "Fits cross at Fm and current of blank",
       x = "Inverse 12C Current (μA-1)",
       y = "Fraction modern") +
  theme_classic() +
  theme_xaringan(title_font_size = 20,
                 text_font_size = 16,
                 background_color = "#ffffff") +
  theme(legend.position = "none",
        legend.background = element_rect(fill = "white", color = "black")) 
```
]

@@

```{r blanks, fig.height=5, dev='svg'}
carb_data %>% filter(fm_consensus < 0.1 &
              Cur > 2) %>% 
  ggplot(aes(Cur, mean)) +
  geom_errorbar(aes(ymin = mean - merr, ymax = mean + merr)) +
  geom_errorbarh(aes(xmin = Cur - Cur.sd, xmax = Cur + Cur.sd)) +
  geom_point(aes(color = wheel), size = 3) +
  labs(title = "Blanks",
       x = "12C Current (μA)",
       y = "Fraction modern") +
  theme_classic() +
  theme_xaringan(title_font_size = 20,
                 text_font_size = 16,
                 background_color = "#ffffff") +
  theme(legend.position = c(0.82, 0.76),
        legend.background = element_rect(fill = "white", color = "black")) 
```

>>>>

dbds %>% 
  filter(Cur < 10) %>% 
  ggplot(aes(fm_consensus, fm_diff)) +
  geom_hline(yintercept = 0) +
  geom_pointrange(aes(ymin = fm_diff - merr, ymax = fm_diff + merr),
                 position = position_dodge2(width = .1),
                 size = .6,
                 color = "#0069b1") +
  labs(title = "Closed inlet",
       x = "Expected Fm",
       y = "Fm difference") +
  theme_classic() +
  theme_xaringan(title_font_size = 20,
                 text_font_size = 16,
                 background_color = "#ffffff")
```
]

@@

# flow vs time subplot
flow_time <- data.frame(x = 0:125) %>% 
  ggplot(aes(x)) +
  stat_function(fun=function(x) concCO2(x, r = 244) * 30, aes(color = "CO2"), size = 1.5) +
  stat_function(fun=function(x) 30 - (concCO2(x, r = 244) * 30), aes(color = "Helium"), size = 1.5) +
  scale_color_manual("Gas", values = c("#00b7bd", "#b7bf10")) +
  labs(title = "Gas flows to source",
       subtitle = "7mL vial, 244μL/min helium, 30μL/min to source",
       y = "Gas flow (μL/min)") +
  theme_classic() +
  theme_xaringan(title_font_size = 20,
                 text_font_size = 18,
                 background_color = "#ffffff") +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        legend.position = c(0.87, 0.65),
        legend.background = element_rect(fill = "white", color = "black"))

# current vs time subplot
cur_time <- ggplot(data, aes(time, he12C)) +
  geom_smooth(span = .4, se=FALSE, color = "#00b7bd") +
  geom_point(size = 3, color = "#0069b1") +
  xlim(0, 125) +
  labs(title = "Ion current",
       x = "Time (min)",
       y = "12C current (μA)") +
  theme_classic() +
  theme_xaringan(title_font_size = 20,
                 text_font_size = 18,
                 background_color = "#ffffff")

@@

.pull-right[
<br>
<br>
<br>
```{r cur-flow-os, fig.height=6, dev='svg'}
ggplot(data, aes(co2flow, he12C)) +
  geom_smooth(span = .3, se=FALSE, color = "#00b7bd") +
  geom_point(size = 3, color = "#0069b1") +
  labs(title = "Vial dillution current",
       subtitle = "250μL/min displacement, 30μl/min delivery",
       x = bquote('CO'[2]~'Flow (μl/min)'), 
       y = "12C current (μA)") +
  theme_classic() +
  theme_xaringan(title_font_size = 20,
                 text_font_size = 16,
                 background_color = "#ffffff")
```
]

@@

livefm_cur <- data %>% 
  filter(!(he12C < 2.5 & normFm > 1.05) & fm_consensus > 0.9) %>% 
  ggplot(aes(he12C, normFm)) + 
  geom_point(size = 2, color = "#0069b1") +
  xlim(0, xl) +
  ylim(.8, 1.2) +
  ggtitle("Ratio vs current") +
  theme_classic() +
  theme_xaringan(title_font_size = 20,
                 text_font_size = 18,
                 background_color = "#ffffff") +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        axis.text.x = element_blank())

deadfm_cur <- data %>% 
  filter(fm_consensus < 0.1 & normFm < 0.3 & Sample.Name != "DilDeadGas6") %>% 
  ggplot(aes(he12C, normFm)) + 
  geom_point(size = 2, color = "#00a9e0") +
  xlim(0, xl) +
  ylim(0, .4) +
  xlab("12C Current (μA)") +
  theme_classic() +
  theme_xaringan(title_font_size = 20,
                 text_font_size = 18,
                 background_color = "#ffffff")

@@

```{r blank-model, fig.height = 4, dev='svg'}
# Plot of data and model with measured blanks
ggplot(ds, aes(Cur_inv, mean, color = Gas)) +
  geom_abline(slope = blankfit$LiveGas_Cur_inv, 
              intercept = blankfit$`LiveGas_(Intercept)`,
              color = "#0069b1") +
  geom_abline(slope = blankfit$DeadGas_Cur_inv, 
              intercept = blankfit$`DeadGas_(Intercept)`,
              color = "#00a9e0") +
  geom_pointrange(aes(ymin = mean - merr, ymax = mean + merr), size = .3) + 
  scale_color_manual("Gas", values = c("#b7bf10", "#00a9e0", "#0069b1")) +
  xlim(0, 10) +
  labs(title = "Modelled blank",
       subtitle = "Fits cross at Fm and current of blank",
       x = "Inverse 12C Current (μA-1)",
       y = "Fraction modern") +
  theme_classic() +
  theme_xaringan(title_font_size = 20,
                 text_font_size = 16,
                 background_color = "#ffffff") +
  theme(legend.position = "none",
        legend.background = element_rect(fill = "white", color = "black"))

factor(ds$Gas)
```
]

@@

```{r blanks, fig.height=5, dev='svg'}
carb_data %>% filter(fm_consensus < 0.1 &
              Cur > 2) %>% 
  ggplot(aes(Cur, mean)) +
  geom_errorbar(aes(ymin = mean - merr, ymax = mean + merr)) +
  geom_errorbarh(aes(xmin = Cur - Cur.sd, xmax = Cur + Cur.sd)) +
  geom_point(aes(color = wheel), size = 3) +
  scale_color_manual("wheel", values = c("#b7bf10", "#00a9e0", "#0069b1")) +
  labs(title = "Blanks",
       x = "12C Current (μA)",
       y = "Fraction modern") +
  theme_classic() +
  theme_xaringan(title_font_size = 20,
                 text_font_size = 16,
                 background_color = "#ffffff") +
  theme(legend.position = c(0.82, 0.76),
        legend.background = element_rect(fill = "white", color = "black")) 
```
